%-------------------------
% Resume in Latex
% Author : Tejas Khairnar
%------------------------

%---- Required Packages and Functions ----

\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage{xcolor}
\usepackage{float}
\usepackage{ragged2e}
\usepackage[empty]{fullpage}
\usepackage{wrapfig}
\usepackage{lipsum}
\usepackage{tabularx}
\usepackage{titlesec}
\usepackage{geometry}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{multicol}
\usepackage{graphicx}
\usepackage{cfr-lm}
\usepackage[T1]{fontenc}
\usepackage{fontawesome}
\usepackage[most]{tcolorbox}


% Set the margins
\geometry{left=0.85cm, top=0.8cm, right=0.85cm, bottom=0.2cm}


% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-7pt}]


%-------------------------
% Custom commands

\newcommand{\resumePOR}[3]{
\vspace{0.5mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{-3mm}{#1}:\hspace{1mm} & \hspace*{0pt}\hfill{\footnotesize{ #3}} \vspace{-0.5mm}\\ \hspace{-2.9mm}#2 
    \end{tabular*}
    \vspace{0mm}
}

\newcommand{\resumeExp}[4]{
\vspace{1mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-1.2mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-6.1mm}
}

\newcommand{\resumeProject}[4]{
\vspace{1mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.4mm} \small\textbf{#1} & {\footnotesize{#3}}\vspace{-0.5mm}\\
        \hspace{-4.3mm} \footnotesize{\text{#2}} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-4.5mm}
}

\newcommand{\resumeEdu}[4]{
\vspace{0mm}\item[]
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \hspace{-4.3mm} \small\textbf{#1} & \footnotesize{#3}\vspace{-1mm} \\
        \hspace{-4.3mm} \footnotesize{#2} & \footnotesize{#4}
    \end{tabular*}
    \vspace{-3.2mm}
}

\newcommand{\resumeAchieve}[3]
{
\hspace{-3.1mm}\textbf{ #1} & {#2} & \hspace{3mm}\footnotesize{#3}
\vspace{0mm}\\
}


\renewcommand{\labelitemi}{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*,labelsep=0mm,itemsep=-2.5mm]}

\newcommand{\resumeItemListStart}{\begin{justify}\begin{itemize}[leftmargin=3ex, rightmargin=2ex, noitemsep,labelsep=1.2mm,itemsep=0mm]\small}

\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-2mm}}
\newcommand{\resumeItemListEnd}{\end{itemize}\end{justify}\vspace{-1.5mm}}

\renewcommand{\arraystretch}{1}

\newcolumntype{L}{>{\raggedright\arraybackslash}X}%
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}%
\newcolumntype{C}{>{\centering\arraybackslash}X}%
%---- End of Packages and Functions ------



%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%

\newcommand{\name}{Sakshi Agrawal} % Your Name
\newcommand{\course}{Integrated M.Sc. in Economics} % Your Course
\newcommand{\roll}{20HS20061} % Your Roll No.
\newcommand{\phone}{8529161117} % Your Phone Number
\newcommand{\emaila}{sakshiagrawal1651@gmail.com} %Email 1
\newcommand{\github}{swabhi-iitkgp} %Github
\newcommand{\website}{https://example.com} %Website
\newcommand{\linkedin}{sakshi-agrawal-1856a4213/} %linkedin



\begin{document}
\fontfamily{cmr}\selectfont


%----------HEADING-----------------
\begin{center}
    \LARGE{\textbf{\name}}
\end{center}
\vspace{-6.5mm}
\begin{center}
    \small{ \href{https://www.linkedin.com/in/\linkedin/}{\faLinkedinSquare \hspace{0.2mm} linkedin.com/in/sakshi-agrawal-1856a4213/} | \href{mailto:\emaila}{\faSend \hspace{0.2mm} \emaila} | \faPhone \hspace{0.2mm} +91-\phone }
\end{center}
\vspace{-3mm}

%-----------EDUCATION-----------------

\vspace{-2.5mm}
% \section{Education}
%   \resumeSubHeadingListStart
%     \resumeSubheading
%       {Indian Institute of Technology Guwahati}{Guwahati, India}
%       {Bachelor of Technology in Mathematics and Computing ;  GPA: 8.10}{July. 2015 -- July. 2019 (Expected)}
%     \resumeSubheading
%       {Burdwan Model School}{Burdwan, W.B}
%       {Central Board of Secondary Education (Class XII);  Percentage: 96.60}{March. 2015}
%   \resumeSubHeadingListEnd\vspace{-3mm}
\section{Education}
\setlength{\tabcolsep}{5pt} % Default value: 6pt
% \renewcommand{\arraystretch}{1.1} % Default value: 1
\small{\begin{tabularx}
{\dimexpr\textwidth-3mm\relax}{|c|C|c|}
  \hline
  \textbf{Degree/Certificate } & \textbf{Institute/Board} & \textbf{CGPA/Percentage}\\
  \hline
  Integrated M.Sc. & Indian Institute of Technology, Kharagpur & 8.64\\
  
  \hline
  Senior Secondary & CBSE Board & 88.6\% \\
  \hline
  Secondary & CBSE Board & 10.00 \\
  \hline
\end{tabularx}}
\vspace{-2mm}



%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeProject
{Venture Capital Experience Project} %Project Name
{Quollab} %Project Name, Location Name
{February 2021 - March 2021} %Event Dates
{\href{https://quollab.com/}{Link to Quollab website.}} %Website
\resumeItemListStart
\item[$\bullet$] Headed a team of 5 members and participated in the due diligence process.
\item[$\bullet$] Did strong sector research of the EdTech sector and led virtual investments.

\resumeItemListEnd

\resumeProject
{Bluetooth-enabled Automatic Plant Watering System}
{Prof.  Vikrant Racherla,  IIT Kharagpur} %Project Name, Location Name
{March 2021 - June 2021} %Event Dates
{\href{https://youtu.be/vSBbuox9BX4}{Link to the project video.}} 
\resumeItemListStart
\item[$\bullet$] Created a Bluetooth-enabled automatic plant watering system useful for maintaining small household gardens.
\item[$\bullet$] Used soil moisture sensor to control water flow through Arduino.
\item[$\bullet$] Used a Bluetooth module to enable control through a mobile application.
\resumeItemListEnd

\resumeProject
{Case Study 
}
{ShARE, IIT Kharagpur} %Project Name, Location Name
{November 2021 - December 2021} %Event Dates
{\href{https://drive.google.com/drive/folders/1T-zYbgaR85XATaBYmwf45kFPz2gli375?usp=share_link}{Link to the presentation.}} 
\resumeItemListStart
\item[$\bullet$] Analysed and presented a case study on whether TATA should buy Air India and did SWOT analysis for the same.
\item[$\bullet$] Worked on a case study that was examined to show how technical and vocational education may be developed in India to help the lower classes.

\resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-5.5mm}


\section{Technical Skills}
\vspace{0.2mm}

\small{\begin{tabular*}{\textwidth}[t]{p{0.5\textwidth} p{0.5\textwidth}}

\hspace{-3.1mm}{\textbf{ Programming languages:} C, Python, STATA}  \\  
\hspace{-3.1mm}{\textbf{ Libraries:} Sklearn, Numpy, Pandas, Matplotlib} \\
\hspace{-3.1mm}{\textbf{ Miscellaneous skills:} MATLAB, MS Excel, MS PowerPoint} 
\end{tabular*}}

\vspace{-2.5mm}
\section{Relevant Coursework}
\vspace{0.2mm}


\small{\begin{tabular*}{\textwidth}[t]{p{\textwidth}}
\hspace{-3.1mm}\textbf{ Finance: }{Trading Basics, Varsity by Zerodha, Bloomberg Market Concepts, Econometric Analysis, Financial Management, Financial Analysis, Corporate Valuation and Restructuring}\\
\hspace{-3.1mm}\textbf{ Miscellaneous Courses: }{Operations Research, Programming and Data Structures, Probability and Statistics, Statistics for Economics}
\end{tabular*}}

\vspace{-2.5mm}

\section{Position of Responsibilty}
\vspace{0.2mm}

\textbf{Associate Manager | Entrepreneurship Cell, IIT Kharagpur}\hspace {65mm}{May 2021 - April 2022}
\resumeItemListStart
\item[$\bullet$]Part of the largest student-run, non-profit organisation, started in 2006, which works with the aim of fostering
innovation and entrepreneurship in India. I handled the Corporate and Media Relations portfolio which keeps me in
dialogue with top CXOs in India and attained corporate and media partnerships for the cell.
\item[$\bullet$] Single-handedly organised the Bhopal chapter of Entrepreneurship Awareness Drive 2021 by partnering with the
top 2 local universities and inviting speakers from prominent organisations like Co-founder, Signzy and Founder,
SayTrees.
\item[$\bullet$] Led a team of 15 Campus Ambassadors to publicise the event in Bhopal and nearby cities.
\item[$\bullet$] Attained sponsorship worth INR 6,00,000 from companies like Cisco, ITC Limited etc. and associated with media
bodies like Business Standard, The Indian Express, Amar Ujala and YourStory.
\item[$\bullet$] Collaborated with international organisations to launch outdoor advertising in UAE and US.
\resumeItemListEnd

\hspace{-6.1mm}{\textbf{General Secretary, Social and Cultural | SN/IG Hall of Residence}}\hspace{55mm}{May 2022 - Present}
\resumeItemListStart
\item[$\bullet$] Managed an annual social and cultural activities budget of INR 6.43 Lakhs at SN/IG Hall of Residence, IIT Kharagpur.
\item[$\bullet$] Coordinated with fellow General Secretaries to manage a team of 100+participants in Interhall Illumination.
\item[$\bullet$] Ensured practice and participation of 30+ boarders in Interhall Rangoli Competition.
\item[$\bullet$] Managed participation of 100+ boarders in 18 inter-hall competitions in General Championship 2022-2023.
\item[$\bullet$] Organized events on occasions of Independence Day, Republic Day and Saraswati Pooja.
\resumeItemListEnd


\vspace{-2.5mm}

\section{Achievements}
\vspace{0.2mm}

\resumeItemListStart
\item[$\bullet$] Competed with 10 Lakh students all over India and qualified JEE Advanced.
\item[$\bullet$] Secured the position of Departmental Rank 2 in 4th semester.
\item[$\bullet$] Secured the 2nd position in interhall Choreography and Rangoli competions.
\resumeItemListEnd


\vspace{-2.5mm}

\vspace{0mm}

%-------------------------------------------
\end{document}